---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  message = FALSE,
  warning = FALSE
)
```

# RRRR

<!-- badges: start -->
[![Build\_Status](https://travis-ci.org/FinYang/RRRR.svg?branch=master)](https://travis-ci.org/FinYang/RRRR)
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/RRRR)](https://cran.r-project.org/package=RRRR)
[![Monthly\_Downloads](http://cranlogs.r-pkg.org/badges/RRRR)](https://cran.r-project.org/package=RRRR)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
<!-- badges: end -->

The R package *RRRR* provides methods for estimating online Robust Reduced-Rank Regression.

To cite package ‘RRRR’ in publications use:

>  Yangzhuoran Yang and Ziping Zhao (2020). RRRR: Online Robust   Reduced-Rank Regression Estimation. R package version 1.0.0. https://pkg.yangzhuoranyang.com/RRRR/.

## Installation

You can install the **stable** version on [R CRAN](https://CRAN.R-project.org/package=RRRR).

```{r cran-installation, eval = FALSE}
install.packages("RRRR")
```


You can install the **development** version from [Github](https://github.com/FinYang/RRRR) with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("FinYang/RRRR")
```

## Usage

The R package *RRRR* provides the following estimation methods.

1. Reduced-Rank Regression using Gaussian MLE: `RRR`
2. Robust Reduced-Rank Regression using Cauchy distribution and Majorisation-Minimisation: `RRRR`
3. Online Robust Reduced-Rank Regression: `ORRRR`
    - SMM: Stochastic Majorisation-Minimisation
    - SAA: Sample Average Approximation
4. Online update of the above model (except `RRR`): `update.RRRR`

See the vignette for a more detailed illustration.

```{r}
library(RRRR)
set.seed(2222)
data <- RRR_sim()
res <- ORRRR(y=data$y, x=data$x, z=data$z)
res
plot(res)

newdata <- RRR_sim()
res2 <- update(res, newy=newdata$y, newx=newdata$x, newz=newdata$z)
res2
```



## License

This package is free and open source software, licensed under GPL-3.
